---
title: "lab_01"
author: "Derek Willis"
date: "2023-01-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Turn off scientific notation
options(scipen=999)
```

## About this lab

To complete this lab, you need to: \* run existing code as directed (look for **Task**). \* modify existing code as directed (look for **Task**). \* write code in empty codeblocks provided to answer questions included (look for **Q**). \* write out the answer in the form of a complete sentence in the space given (look for **A**). When you are finished, commit changes and push to your personal GitHub repo, then submit the URL to this document on ELMS.

Remember to add any new verbs or concepts to your class reference notebook!

## Load libraries and establish settings

**Task** Run the codeblock below to load the Tidyverse. To run the codeblock, hit the little green play button in the upper right corner of the gray area (the codeblock) below.

```{r}
# Load the tidyverse. If you have not installed the tidyverse already, remove the # from the next line and run it first.  
# install.packages('tidyverse')
library(tidyverse)
```

## Load Data

We're going to load the UMD courses data.

**Task** Run the codeblock below to load the data, which is contained in an RDS file.

```{r}
umd_courses <- read_rds("lab_01.rds")
```

## Answer questions

**Q1** Which department has the highest mean (average) number of seats for its classes? You need to show the department with the highest average first. Which one is the most surprising/interesting to you? **A1**

`I believe that Business and Management has the highest mean number of seats for its classes. The number that business and management had for its mean seats was 162813. The course that is most surprising to me in terms of average seats is engineering, mechincal with 28.911124 mean seats.`

```{r}
umd_courses |>
  group_by(term) |>
  summarise(
    mean_seats =mean(seats),
  )

```

**Q2** Find out the greatest number of times any individual class has been offered in our dataset. Your code must show the greatest number of classes first. **A2**

Business and Management has the greatest number of times any individual class has been offered with 4975 times.

```{r}
umd_courses |>
  group_by(department) |>
  summarise(
    count_classes = n(),
  )
```

**Q3** Count the number of courses for each instructor and department. Which instructor has taught the most? **A3**

The instructor who has taught the most is Keith Yearwood and the department is Geographical Sciences. Keith Yearwood has taught 61 courses.

```{r}
umd_courses |>
  group_by(department, instructors) |>
  summarise(
    count_classes = n(),
  ) |>

arrange(desc(count_classes))

```

**Q4** Given the results for Q3, what would have made it easier to find the answer? You don't have to know *how* to accomplish this; I want you to describe in words what would make the answer easier to see. How confident are you that the answer you got is the right one, and why? **A4**

To find the answer easier, I would have sorted it by instructors that are listed rather than all courses showing because that gave me instructors who were not listed. I feel pretty confident that I got this question correct mainly because once I arranged it, I was able to scroll through the instructors and find the first one that popped up.

**Q5** Take one of the questions you listed in the final question of the pre_lab and try to answer it here in code. If you don't know how to fully answer it, write what code you can and describe in words what else you would need to do. If you got an answer, is it interesting? **A5**

```{r}
umd_courses |>
  group_by(department) |>
  summarise()


    
```

I understand how to start this line of code and how it has the ability to help me answer why chemistry has fewer classes but more seats compared to information studies, which has more classes but fewer seats, but from there, I'm not sure how to code the rest. I believe I would need to have total_seats and then in parentheses the courses and then sort the data with the arrange function to have this all written out in code.
